Verifying Demonstrations

### 2018-11-19 paper/intro.tex
adds some comments, moves gvt id remarks from system model to discussion
Adds missing space

\emph{Context.} 
Consider the following scenario.
Alice is an activist that organizes a protest in some location(s) against the current government, represented by Grace.
On the one hand, Alice wants to estimate the number of participants to prove a certain support for her cause.
On the other hand, Grace is an autocratic regime leader who opposes Alice's cause.
Bob, Carol and many others participate in the protest for Alice's cause against Grace.
However, they might only be willing to do so in a manner that does not leave any digital traces because of the fear of retribution against them from Grace's regime. 
To realize this objective, a reliable yet privacy-preserving crowd-counting mechanism is needed, which to the best of our knowledge is a problem that has not yet been entirely solved as of today.

@@

The paper is organized as follows.
First, in \cref{system-model}, we describe our system model and summarize the desired properties for crowd counting. Next, in \cref{related-work}, we discuss related work in terms of these properties, first the crowd counting methods that are classically used and then work on location proof systems that inspired \CROCUS. 
We then formalize the notion of protest and the desired verifiability and privacy properties, and in \cref{building-blocks}, we give the relevant background on the building blocks of our solution. 
Afterwards, in \cref{DB-anon-cred}, we present a new \ac{DB} version of the Schnorr protocol, different from that originally proposed by \textcite{DistanceBounding}.
We provide a proof of its security (\ie the fact that it achieved all desired \ac{DB} properties) 
\daniel{Check that this is true before publication.} 
and formally verify it using Tamarin~\cite{TamarinDB}.
\seb{we need to be careful about the above sentence}
%This version of the Schnorr protocol can then be used to do general \ac{DB} anonymous credentials.
Then in\cref{Protocol}, we present \CROCUS, a privacy-preserving crowd counting estimation protocol constructed from these building blocks, before analyzing its security and privacy (\cref{SecurityAnalysis}).
Finally, we discuss our assumptions and results \cref{Discussion} and give our conclusions in \cref{Conclusion}.
%\sonja{add (sub) sections for performance and verification}

>>>>

\emph{Context.}

\sonja{explain that this is for crowd counting in general, but we choose a scenario where privacy and verifiability (transparency) matter most: protest against oppressive regime}
Consider the following scenario.
Alice is an activist that organizes a protest in some location(s) against the current government, represented by Grace.
On the one hand, Alice wants to estimate the number of participants to prove a certain support for her cause.
On the other hand, Grace is an autocratic regime leader who opposes Alice's cause.
Bob, Carol and many others participate in the protest for Alice's cause against Grace.
However, they might only be willing to do so in a manner that does not leave any digital traces because of the fear of retribution against them from Grace's regime. 
To realize this objective, a reliable yet privacy-preserving crowd-counting mechanism is needed, which to the best of our knowledge is a problem that has not yet been entirely solved as of today.

@@

The paper is organized as follows.
First, in \cref{system-model}, we describe our system model and summarize the desired properties for crowd counting. Next, in \cref{related-work}, we discuss related work in terms of these properties, first the crowd counting methods that are classically used and then work on location proof systems that inspired \CROCUS. 
We then formalize the notion of protest and the desired verifiability and privacy properties, and in \cref{building-blocks}, we give the relevant background on the building blocks of our solution. 
Afterwards, in \cref{DB-anon-cred}, we present a new \ac{DB} version of the Schnorr protocol, different from that originally proposed by \textcite{DistanceBounding}.
We provide a proof of its security (\ie the fact that it achieved all desired \ac{DB} properties) 
\daniel{Check that this is true before publication.} 
and formally verify it using Tamarin~\cite{TamarinDB}.
\seb{we need to be careful about the above sentence}
%This version of the Schnorr protocol can then be used to do general \ac{DB} anonymous credentials.
Then in \cref{Protocol}, we present \CROCUS, a privacy-preserving crowd 
counting estimation protocol constructed from these building blocks, before 
analyzing its security and privacy (\cref{SecurityAnalysis}).
Finally, we discuss our assumptions and results \cref{Discussion} and give our conclusions in \cref{Conclusion}.
%\sonja{add (sub) sections for performance and verification}
